---
title: Homework 5
subtitle: Data Visualization and Data Transformation
date: last-modified
from: markdown+emoji
comments: false
code-fold: false

execute: 
  warning: false
  message: false
  fig-width: 9
  fig-height: 7
  fig-align: center
---
```{r}
#| eval: true
#| include: false

library(tidyverse)
library(skimr)
```

# Direction

- Provide your answer to questions in **Homework 5** in the `danl-200-hw-05-q.qmd`.

- Please submit your **Quarto document for Homework 5** to the Brightspace with the name below:

  - `danl-200-hw5-LASTNAME-FIRSTNAME.qmd`\
  ( e.g., `danl-200-hw5-choe-byeonghak.qmd` )

- The due is May 9, 2024, 11:59 P.M.

- Please send an email to Byeong-Hak (`bchoe@geneseo.edu`) if you have any questions or clarifications.

<br><br><br>

# Question 1

For Question 1, run the following R command to read the CSV file, `spotify_all.csv` as data.frame, `spotify_all`:

```{r}
#| echo: true
#| eval: true
#| warning: false
#| message: false
spotify_all <- read_csv('https://bcdanl.github.io/data/spotify_all.csv')
```

```{r}
#| echo: false
#| eval: true
rmarkdown::paged_table(spotify_all)
```

<br>

The data.frame `spotify_all` includes information about Spotify users' playlists.

  - The unit of observation in `spotify_all` is a track in a music playlist.

<br>

## Variable Description

- `pid`: playlist ID; unique ID for playlist
  
- `playlist_name`: a name of playlist
  
- `pos`: a position of the track within a playlist (starting from 0)
  
- `artist_name`: name of the track's primary artist
  
- `track_name`: name of the track
  
- `duration_ms`: duration of the track in milliseconds
  
- `album_name`: name of the track's album

<br>

## Q1a

- Find the ten most popular song.
  - A value of a song is defined as a combination of a `artist_name` value and a `track_name` value. 
  - Who are artists for those ten most popular song?

*Answer:*
```{r}

```

<br><br>

## Q1b

-   Find the five most popular artist in terms of the number of occurrences in the data.frame, `spotify_all`.
-   What is the most popular song for each of the five most popular artist?


*Answer:*
```{r}

```

<br><br>


## Q1c
- Create a data.frame named `drake_one_dance` that includes all playlists featuring the song where `track_name` equals "One Dance" and `artist_name` equals "Drake".
  - Ensure that the data.frame `drake_one_dance` does not contain any playlists where the song "One Dance" by Drake is absent.

- What is the song with the highest frequency of appearances after Drake’s “One Dance” in the newly created data.frame, `drake_one_dance`?

*Answer:*
```{r}

```

<br><br>


## Q1d

Provide both (1) ggplot code and (2) a couple of sentences to describe the relationship between `pos` and the ten most popular artists.


*Answer:*
```{r}

```

<br><br>

## Q1e
Create the data.frame with `pid`-`artist` level of observations with the following four variables:

-   `pid`: playlist id
-   `playlist_name`: name of playlist
-   `artist`: name of the track's primary artist, which appears only once within a playlist
-   `n_artist`: number of occurrences of artist within a playlist


*Answer:*
```{r}

```

<br><br><br>

# Question 2. Climate Finance

- Climate finance refers to local, national or transnational financing—drawn from public, private and alternative sources of financing—that seeks to support mitigation and adaptation actions that will address climate change ([https://unfccc.int/topics/introduction-to-climate-finance](https://unfccc.int/topics/introduction-to-climate-finance)).

  - Mitigation involves taking actions to reduce the emissions of greenhouse gases that are responsible for climate change.
  - Adaptation involves taking actions to reduce the actual or expected damages from climate change ([https://climate.nasa.gov/solutions/adaptation-mitigation](https://climate.nasa.gov/solutions/adaptation-mitigation)).

- Load the data.frame for Question 2.

```{r}
#| eval: true
#| echo: true
path <- 'https://bcdanl.github.io/data/climate_finance_energy.csv'
climate_finance <- read_csv(path)
```

<br>

```{r}
#| echo: false
#| eval: true
#| results: asis
rmarkdown::paged_table(climate_finance) 
```

<br>

- A unit of observation in `climate_finance` data.frame is a climate change project.

<br>

## Variable Description

- `Party`: a party (country) that provides a funding contribution to recipient country/region for their cliamte change project.

- `Recipient country/region`:  Recipient country or region

- `Project/programme/activity`:  Details in the climate change project

- `Type of support`:  
  - `adaptation` if the climate change project is related to adaptation project.
  - `mitigation` if the climate change project is related to mitigation project.
  
- `Year`: Year that funding contribution is committed or provided.

- `Contribution`: An amount of funding contribution for the climate change project (in USD).

- `Status`: 
  - `committed` if a party commits to providing the funding contribution for the climate change project, but the funding contribution is NOT actually provided.
  - `provided` if the funding contribution was provided for the climate change project.
  
- `Energy`: 
  - `TRUE` if the project is energy-related; 
  - `FALSE` otherwise.


## Q2a

How many `parties` have provided positive financial `contributions` to other `countries/regions` for their `adaptation` projects for every year between 2011 and 2018?


*Answer:*
```{r}

```

<br><br>


## Q2b

Provide both (1) ggplot code and (2) a simple comment to describe how the yearly trend of total funding `Contribution` varies by `Energy` and `Status`.


*Answer:*
```{r}

```

<br><br>


## Q2c

For each `party`, calculate the total funding `contributions` that were `provided` for `mitigation` projects for each `year`.


*Answer:*
```{r}

```

<br><br>





<br><br><br>

# Question 3  

## Q3a
- Write and publish a blog post on your GitHub website, featuring data analysis based on the `spotify_all` data.frame in Question 1 in Homework 5.
  - Ensure that the blog post has an appropriate thumbnail by including an image file in the blog post's directory with a proper YAML header option.
  
```{r}
#| eval: false
spotify_all <- read_csv('https://bcdanl.github.io/data/spotify_all.csv')
```

<br><br>


## Q3b
  - Ensure that the blog post assigned in Homework 4 has an appropriate thumbnail by including an image file in the blog post's directory with a proper YAML header option.
  
<br><br>

